Coherent optical association of a single molecule

### 2020-10-20 paper.tex
Remove figure 2c (merged into 3a)

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure*}[ht!]
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
    using a $0.12\mathrm{ms}$ pulse.
    The full width half maximum (FWHM) of $7.56(82) \mathrm{kHz}$ of the resonance
    is consistent with the FWHM for a coherent $0.12\mathrm{ms}$ $\pi$ pulse $6.7 \mathrm{kHz}$.
    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
    proving the coherence of the Raman transfer process.
    \label{f-raman}}
\end{figure*}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$ which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step, so successful transfer of the atoms to the molecular state will be detected as loss of atoms in the post experiment image when compared to the initial image. We observed the narrowest linewidth of $7.56(82) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.12 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.907(98)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is evidence of a coherent transfer. In order to verify the coherence of the transfer directly, we fix the two photon detuning on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $69\%$ of initial ground state atoms are transferred into the molecular state.

>>>>

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.45\textwidth]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
    proving the coherence of the Raman transfer process.
    \label{f-raman}}
\end{figure}

@@

Guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss of atoms
in the post experiment image when compared to the initial image.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.
